Deep Learning

### 2015-01-07 deepreview.tex
updating bib entries and references cleanup

Backpropagation provides an efficient way of computing gradients for all of
the weights in a layered network on a single training case, but there are
still many ways to make use of these gradients. The most obvious method is
to average the gradients over all of the cases in the training set and then
to change each weight in proportion to its negative gradient, which is the
direction where a small change will most improve the objective function. 
When the training set contains millions of cases and is highly redundant, however,
this is needlessly slow. It is much faster to compute the average gradient
on a small ``mini-batch'' of randomly chosen training cases and to update
each weight by this stochastic estimate of its full gradient times a
learning rate which decays as learning proceeds. Stochastic gradient
descent can be improved by using the history of the individual weight
gradients to adapt the learning rate for each weight\cite{bottou-bousquet}
or to provide additional increments that depend on earlier gradients\cite{momentum}
but these techniques are still the subject of controversy and are beyond
the scope of this review.  However, it is now widely accepted that some
form of stochastic gradient descent is the best bet for large, redundant
datasets.

@@

The connectivity of the network is restricted so that each of the one-of-N
input vectors must first be converted to a ``word-vector'' before being
used by subsequent layers to give a high probability to the target next
word.  The network learns word-vectors that contain many active components
each of which can be interpreted as a separate feature of the word. This
was first demonstrated\cite{RHW} using sequences of three words, such as
(Colin, Mother, Victoria), derived from two family trees. The learned word
vector for Colin contained ``semantic'' features representing which family
tree Colin was in, what branch of that tree he was in, and from what generation
he was~\cite{hinton86}. These semantic features were not explicitly present
in the input.  They were discovered by the learning procedure as a good way
of factorizing the structured relationships between the input and output
symbols into multiple ``micro-rules''.  For example, given Colin's
generation and the learned feature of Mother that the output should be one
generation higher than the input, we can already restrict the answer to
people in a specific generation. The ability of deep learning to discover
many such micro-rules allows it to generalize well to novel combinations of
individually familiar context words.

The family tree demonstration used a small, clean dataset in which the
regularities could be captured by micro-rules that were never violated and
the features were easy to interpret, but learned word-vectors also work
very well when the word sequences come from a large corpus of real text and
the individual micro-rules are unreliable~\citep{BenDucVin01-short}. When trained to
predict the next word in a news story, for example, the learned word
vectors for Monday and Tuesday are very similar, as are the word vectors
for Vietnam and Iraq.  Vector representations of words learned from text
are now very widely used in natural language applications~\cite{Collobert,
  Mikolov, Socher?}.

@@

@@

When deep convolutional networks were applied to a dataset of about a
million images from the web that contained a thousand different classes
they achieved spectacular results, almost halving the error rates of the
best computer vision sytems~\cite{kriz}.  Some of the images and the
network's predictions are shown in figure ??.  The major factors in this
success were the large labeled dataset~\cite{FeiFe}, the use of fast GPUs,
and the convolutional early layers.  It had already been shown that deep
supervised nets with rectified linear units could be trained without
unsupervised pre-training~\citep{Glorot+al-AI-2011-small}. 
These rectified linear units made the
training much faster and the fully connected final layers were prevented
from overfitting the peculiarities of the training set by randomly omitting
hidden units during training~\cite{dropoutJMLR}. Deep convolutional nets
have quickly replaced the carefully engineered pipelines full of
hand-designed features developed by the computer vision community and they
are now deployed in many computer vision applications, including image
tagging, object detection, face recognition, facial expression recognition
and scene parsing.

@@

\section{Key references}
{\it Quite a few of these are very recent and have not yet been published
  through a peer-review so we are giving their arxiv references}.

\subsection{Back-propagation and Stochastic Gradient Descent}

%Rumelhart, D. E., Hinton, G. E., \& Williams, R. J. (1986)\\ Learning
%representations by back-propagating errors.\\ {\it Nature}, {\bf 323},
%533-536.
\citep{Rumelhart86b}

LeCun, Y., Boser, B., Denker, J. S., Henderson, D., Howard, R.E., Hubbard,
W., \& Jackel, L.D.\\ Backpropagation Applied to Handwritten Zip Code
Recognition\\ Neural Computation, 1(4):541-551, Winter 1989

\subsection{Distributed representations}
Hinton, G. E., McClelland, J. L., \& Rumelhart, D. E. (1986)\\ Distributed
representations.\\ In Rumelhart, D. E. and McClelland, J. L., editors, {\it
  Parallel Distributed Processing: Explorations in the Microstructure of
  Cognition. Volume 1: Foundations}, MIT Press, Cambridge, MA. pp 77-109.

>>>>

Backpropagation provides an efficient way of computing gradients for all of
the weights in a layered network on a single training case, but there are
still many ways to make use of these gradients. The most obvious method is
to average the gradients over all of the cases in the training set and then
to change each weight in proportion to its negative gradient, which is the
direction where a small change will most improve the objective function. 
When the training set contains millions of cases and is highly redundant, however,
this is needlessly slow. It is much faster to compute the average gradient
on a small ``mini-batch'' of randomly chosen training cases and to update
each weight by this stochastic estimate of its full gradient times a
learning rate which decays as learning proceeds. Stochastic gradient
descent can be improved by using the history of the individual weight
gradients to adapt the learning rate for each weight~\citep{bottou-bousquet-2008-small}
or to provide additional increments that depend on earlier gradients\cite{momentum}
but these techniques are still the subject of controversy and are beyond
the scope of this review.  However, it is now widely accepted that some
form of stochastic gradient descent is the best bet for large, redundant
datasets.

@@

The connectivity of the network is restricted so that each of the one-of-N
input vectors must first be converted to a ``word-vector'' before being
used by subsequent layers to give a high probability to the target next
word.  The network learns word-vectors that contain many active components
each of which can be interpreted as a separate feature of the word. This
was first demonstrated\cite{RHW} using sequences of three words, such as
(Colin, Mother, Victoria), derived from two family trees. The learned word
vector for Colin contained ``semantic'' features representing which family
tree Colin was in, what branch of that tree he was in, and from what generation
he was~\cite{Hinton-et-al-PDP1986}. These semantic features were not explicitly present
in the input.  They were discovered by the learning procedure as a good way
of factorizing the structured relationships between the input and output
symbols into multiple ``micro-rules''.  For example, given Colin's
generation and the learned feature of Mother that the output should be one
generation higher than the input, we can already restrict the answer to
people in a specific generation. The ability of deep learning to discover
many such micro-rules allows it to generalize well to novel combinations of
individually familiar context words.

The family tree demonstration used a small, clean dataset in which the
regularities could be captured by micro-rules that were never violated and
the features were easy to interpret, but learned word-vectors also work
very well when the word sequences come from a large corpus of real text and
the individual micro-rules are unreliable~\citep{BenDucVin01-short}. When trained to
predict the next word in a news story, for example, the learned word
vectors for Monday and Tuesday are very similar, as are the word vectors
for Vietnam and Iraq.  Vector representations of words learned from text
are now very widely used in natural language applications~\cite{Schwenk-2007,CollobertR2008-short,
Mikolov-Interspeech-2011-small,Socher-2011}.

@@

\citep{LeCun89-small}

@@

When deep convolutional networks were applied to a dataset of about a
million images from the web that contained a thousand different classes
they achieved spectacular results, almost halving the error rates of the
best computer vision sytems~\cite{kriz}.  Some of the images and the
network's predictions are shown in figure ??.  The major factors in this
success were the large labeled dataset~\cite{imagenet_cvpr09}, the use of fast GPUs,
and the convolutional early layers.  It had already been shown that deep
supervised nets with rectified linear units could be trained without
unsupervised pre-training~\citep{Glorot+al-AI-2011-small}. 
These rectified linear units made the
training much faster and the fully connected final layers were prevented
from overfitting the peculiarities of the training set by randomly omitting
hidden units during training~\cite{dropoutJMLR}. Deep convolutional nets
have quickly replaced the carefully engineered pipelines full of
hand-designed features developed by the computer vision community and they
are now deployed in many computer vision applications, including image
tagging, object detection, face recognition, facial expression recognition
and scene parsing.

@@

%\section{Key references}
%{\it Quite a few of these are very recent and have not yet been published
%  through a peer-review so we are giving their arxiv references}.

%\subsection{Back-propagation and Stochastic Gradient Descent}

%Rumelhart, D. E., Hinton, G. E., \& Williams, R. J. (1986)\\ Learning
%representations by back-propagating errors.\\ {\it Nature}, {\bf 323},
%533-536.
% --> \citep{Rumelhart86b}

%LeCun, Y., Boser, B., Denker, J. S., Henderson, D., Howard, R.E., Hubbard,
%W., \& Jackel, L.D.\\ Backpropagation Applied to Handwritten Zip Code
%Recognition\\ Neural Computation, 1(4):541-551, Winter 1989
%--> \citep{LeCun89-small}

%\subsection{Distributed representations}

%Hinton, G. E., McClelland, J. L., \& Rumelhart, D. E. (1986)\\ Distributed
%representations.\\ In Rumelhart, D. E. and McClelland, J. L., editors, {\it
%  Parallel Distributed Processing: Explorations in the Microstructure of
%  Cognition. Volume 1: Foundations}, MIT Press, Cambridge, MA. pp 77-109.
% --> \citep{Hinton-et-al-PDP1986}
